Supercritical fluid extraction of essential oil from chamomile flowers: modelling, and parameter estimation

### 2024-05-04 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Sections/Experiments.tex
04.05

	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to calibrate the model based on the experimental the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers. The experiments were performed by \citet{Povh2001} and \citet{Rahimi2011}. The experiments were conducted using a semi-batch extractor with a diameter of 3.96 [cm] and a length of 16.55 [cm]. Twelve experiments were performed under different operating conditions: $30-40^\circ C$, $100 - 200$ [bar], and $0.12 - 0.24$ [kg/h]. The amount of solid material used for extraction was $75$ [g], which was sufficient to fill the whole vessel. The bulk density of the bed was computed based on the feed's mass and the extractor's volume. The total porosity of the bed, including the particles, was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$. It is assumed that the total amount of the extract is equal 3 [g], defined as to the biggest obtained yield after rounding up.

>>>>

	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to test the process model against the experimental dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers. The experiments were performed by \citet{Povh2001} and \citet{Rahimi2011}. The experiments were conducted using a semi-batch extractor with a diameter of 3.96 [cm] and a length of 16.55 [cm]. Twelve experiments were performed under different operating conditions: $30-40^\circ C$, $100 - 200$ [bar], and $0.12 - 0.24$ [kg/h]. The amount of solid material used for extraction was $75$ [g]. The bulk density of the bed was computed based on the feed's mass and the extractor's volume. The bed porosity was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$. It is assumed that the total amount of the solute equals 3 [g], defined as the largest obtained yield after rounding up.

### 2024-05-04 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Sections/Model.tex
04.05

	\subsubsection{Continuity equation} \label{CH: Continuity}
	 %When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction $\phi$ (where ${\color{black}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}

	%The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function $A_f = A\phi$ to take into account the change of the cross-section available for the fluid. The Equation \ref{EQ: Continuity_differential} shows the differential form of the continuity equation:

	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is refined by incorporating a function $A_f = A\phi$. This modification accounts for the variability in the cross-sectional area available for fluid flow. Equation \ref{EQ: Continuity_differential} presents this adaptation in the differential form of the continuity equation, capturing the dynamics of the flow as it responds to changes in the cross-section.

@@

	%{\color{black}assign a color of v and u}

@@

	{\footnotesize
	\begin{equation}
		v = \cfrac{F}{\rho_f A\phi} 
	\end{equation}
	}

@@

	{\footnotesize
		\begin{equation}
			u = v \phi = \cfrac{F}{\rho_f A }
		\end{equation}
	}

	The fluid density $\rho_f$ can be obtained from an equation of state (Appendix \ref{CH: EOS}) if temperature and thermodynamic pressure are known along $z$. The variation in fluid density may occurs due to pressure or a inlet temperature changes.

@@

	%The comprehensive derivation of the mass balance equation for the fluid phase is detailed in Appendix \ref{CH: Gouverning equations}. 
	This equation accounts for the movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}), which is constrained to the axial direction due to the quasi-one-dimensional approach that considers changes in the void fraction. It is also assumed that the thermodynamic pressure remains constant throughout the device. The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall, leading to a uniform velocity profile across any cross-section perpendicular to the axial direction. Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself. Thus, the mass balance equation include convection, diffusion, and kinetic terms to represent the fluid phase behaviour.

>>>>

	\subsubsection{Continuity equation} \label{CH: Continuity}

	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is redefined by incorporating a function $A_f = A\phi$. This modification distinguishing a constant and varying terms, where the varying term accounts for the changes in the cross-sectional area available for the fluid. Equation \ref{EQ: Continuity_differential} shows the modified continuity equation:

@@

@@

	{\footnotesize
	\begin{equation} \label{EQ:Velocity_1}
		v = \cfrac{F}{\rho_f A\phi} 
	\end{equation}
	}

@@

	{\footnotesize
		\begin{equation} \label{EQ:Velocity_2}
			u = v \phi = \cfrac{F}{\rho_f A }
		\end{equation}
	}

	The fluid density $\rho_f$ can be obtained from an equation of state (Appendix \ref{CH: EOS}) if temperature and thermodynamic pressure are known along $z$. The variation in fluid density may occurs due to pressure or a inlet temperature changes. In non-isothermal case, $\rho_f$ in Equations \ref{EQ:Velocity_1} and \ref{EQ:Velocity_2} is consider to be an average fluid density along the extraction column.

@@

	Equation \ref{Model_fluid}, describes the movement of the solute in the system, which is constrained to the axial direction due to the quasi-one-dimensional assumption. Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself. It is also assumed that the thermodynamic pressure remains constant throughout the device. The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall, leading to a uniform velocity profile across any cross-section perpendicular to the axial direction. Thus, the mass balance equation include convection, diffusion, and kinetic terms to represent the fluid phase behaviour.

### 2024-05-04 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Sections/Parameter_estimation.tex
04.05

	However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $dY(t_i)/dt$ is measured instead of $Y(t_i)$ itself. In such cases, it is assumed that the unobservable error is added to the deterministic derivative $dy(\theta, t_i)/dt$ as shown below

@@

	\begin{table}[h]
		\adjustbox{max width=\columnwidth}{%
			\begin{tabular}{ lccccccc }
				\hline 
				Parameter		&$k_m$[-] 	& $D_i^R\times10^{-13}$[$m^2/s$] 	& $D_e^M\times10^{-12}$[$m^2/s$]	& $\Upsilon$ [-] \\  \hline
				Lower bound		&0	  		& 0 	  			& 0 				& 0 	   		\\ 
				Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			& $+\infty$ 	\\ 
				Initial guesses	&0.1-10		& $0.1-10$ 			& 0.1-10   			& 0.1-10		\\  \hline
		\end{tabular} }
		\caption{Constraints and initial guess}
		\label{tab:Constraints}
	\end{table}

>>>>

	However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $\frac{dY(t_i)}{dt}$ is measured instead of $Y(t_i)$ itself. In such cases, it is assumed that the unobservable error is added to the deterministic derivative $\frac{dy(\theta, t_i)}{dt}$ as shown below

@@

	\begin{table}[h]
		\centering
		%\adjustbox{max width=\columnwidth}{%
			\small{
			\begin{tabular}{ lccccccc }
				\hline 
				Parameter		&$k_m$[-] 	& $D_i^R\times10^{-13}$[$m^2/s$] 	& $\Upsilon$ [-] & $\sigma$		\\  \hline
				Lower bound		&0	  		& 0 	  							& 0 		  	 & 0			\\ 
				Upper bound		&$+\infty$	& $+\infty$ 						& $+\infty$		 & $+\infty$ 	\\ 
				Initial guesses	&0.1-10		& $0.1-10$ 							& 0.1-10    	 & 0.1-10		\\  \hline
		\end{tabular} }
		\caption{Constraints and initial guess}
		\label{tab:Constraints}
	\end{table}

### 2024-05-04 SFE_article_Parameter_Estimation_short_no_axial_diff- Chamomile/Sections/Results_Chamomile.tex
04.05

	To solve the parameter estimation problem, the single shooting method was used to transform the boundary-value problem into the initial value problem and to formulate the non-linear programming problem. This non-linear optimization task was tackled using the CasADi framework (\citet{Andersson2018}). Each time series was fitted separately to the model with the linear extraction kinetics (Equation \ref{Model_kinetic_no_sat}). The initial value problem was solved multiple times with varying initial guesses to identify the global minimum. In case of the linear, two parameters remain to be determined: the partition coefficient $k_m$ and the internal diffusion coefficient $D_i$.

	Figure \ref{fig: Fit_1_linear} shows the parameter space and corresponding values of the cost function for experiment 1 ($40^\circ C$, 100 bar and 6.67$\times 10^{-5}$ kg/s). As the cost function is to be minimized, the lowest value of $-\ln(L)$ indicate the best fit. A black vertical stripe at $D_i \approx 0.2$ can be observed. That stripe indicates the existence of the optimal value of the $D_i$. In the direction of $k_m$, the cost function is almost flat, which suggests that any value of $k_m$ above 0.1 fits the data equally well. If $k_m$ can be an arbitrary point, then it can grow to infinity, which suggests that the solvent is far from the saturation, and the model can be simplified. The model reduction can be introduced by considering the limit of $k_m$ in the extraction kinetic term:

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.48\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_Space_Linear_Dataset_1.png}
			\caption{The linear kinetic model \\ ~}
			\label{fig: Fit_1_linear}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.48\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_Space_Di_Dx_Dataset_1.png}
			\caption{The reduced linear kinetic model with axial diffusion}
			\label{fig: Fit_1_Di_Dx}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.48\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
			\caption{The modified model}
			\label{fig: Fit_1_Di_Gamma}
		\end{subfigure}
		\caption{Parameter space for experiment 1}
		%\label{fig: Fit_Di_Gamma}
	\end{figure}

@@

	The extraction model can be adapted to incorporate adjustments for the reduced kinetic term and axial diffusion. In this revised setup, two parameters remain undetermined: the internal diffusion coefficient $D_i$ and the axial diffusion coefficient $D_e^M$. Figure \ref{fig: Fit_1_Di_Dx} illustrates the parameter space of the modified model and associated cost function values.

	Similarly to the previous case, the optimal value of $D_i$ exists, but a unique value for the $D_e^M$ cannot be determined. Figure \ref{fig: Fit_1_Di_Dx} illustrates the minimal impact of the axial diffusion coefficient, where a broad range of $D_e^M$ yields identical cost function values. By selecting a low value $D_e^M$, the axial diffusion terms can be reduced or eliminated from the model without compromising its generality. This observation aligns with the findings of \citet{Rahimi2011}, who analysed the same dataset and reported Peclet numbers ranging between 290 and 400. Such high values of the Peclet number suggest that the advection term dominates the mass transfer, and the axial diffusion is negligible.

	In both scenarios previously discussed, the fitting outcomes were not deemed satisfactory. Building upon the concepts underlying the Broken-and-Intact and Shrinking Core models (detailed in Chapter \ref{CH: Gamma_Function}), the $\gamma$-function is introduced to capture the decreasing extraction kinetics. The correction factor is combined with the simplified linear model, resulting in a two-parameter model ($D_i^R$ and $\Upsilon$) as given by Equation \ref{Model_kinetic}. Figure \ref{fig: Fit_1_Di_Gamma} shows the parameter space and the corresponding cost function values.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.66\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
			\label{fig: Fit_1_4_Di_Gamma}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.66\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
			\label{fig: Fit_5_8_Di_Gamma}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.66\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
			\label{fig: Fit_9_12_Di_Gamma}
		\end{subfigure}
		\caption{Parameter estimation results obtained from the modified model}
		\label{fig: Fit_Di_Gamma}
	\end{figure}

@@

	\iffalse
	The estimated parameters describe the diminishing trend of the internal diffusion coefficient $D_i$, as delineated by Equation \ref{EQ: C_sat_function}. It is hypothesized that the internal diffusion coefficient decreases because solute particles face greater difficulty diffusing from the core of a particle than from positions closer to the surface. Decay patterns under various operational conditions, depicted in Figure \ref{fig: Gamma_function}, show that the internal diffusion coefficient is notably higher in fluids under high pressure. This observation aligns with the findings of \citet{Giddings1968}, \citet{Gurdial1989}, and \citet{Machida2011}, who explored the solvation capability of solvents and its correlation with the physical properties of CO$_2$ by calculating the Hildebrand solubility parameter $\delta_H$. \citet{Giddings1968} introduced a correlation for the solubility parameter $\delta_H[\text{MPa}^{1/2}] = 1.25 P_c^{1/2}\rho_r$, with $P_c$ and $\rho_r$ representing the critical pressure and reduced density, respectively. Similarly, \citet{Marcus2006} formulated a correlation based on the Van der Waals equation of state: $\delta_H[\text{MPa}^{1/2}] = 2.79 P_c^{1/4}T_r^{1/4}\rho_r$. As Figure \ref{fig: Gamma_function} shows, fluids with higher solubility factors exhibit greater internal diffusion coefficients. However, the relationship between $\delta_H$ and $D_i$ should be considered indicative rather than definitive due to the non-ideal nature of the system and the omission of external factors such as fluid velocity.

	\begin{figure}[!h]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Gamma_function.png}
		\caption{The decaying internal diffusion coefficient}
		\label{fig: Gamma_function}
	\end{figure}

	\fi

@@

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.48\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Di_Re.png}
			\caption{Linear regression $D_i^R = f(Re)$}
			\label{fig: Correlations_Di_Re}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.48\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Gamma_Re.png}
			\caption{Linear regression $\Upsilon = f(Re)$}
			\label{fig: Correlations_Gamma_Re}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.48\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Di_Re_F.png}
			\caption{Multiple linear regression $D_i^R = f(Re, F)$}
			\label{fig: Correlations_Di_Re_F}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.48\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Gamma_Re_F.png}
			\caption{Multiple linear regression $\Upsilon = f(Re, F)$}
			\label{fig: Correlations_Gamma_Re_F}
		\end{subfigure}
		\caption{Empirical correlations between parameters}
		%\label{fig: Correlations_surface}
	\end{figure}

	In Figures \ref{fig: Correlations_Di_Re} and \ref{fig: Correlations_Gamma_Re}, two distinct data clusters emerge, each corresponding to a different mass flow rate. Despite the linear trends observed in both sets of correlations, the correlations for $D_i^R$ exhibit a decline with increasing Re, whereas those for $\Upsilon$ show an upward trend with Re. The decrease in $D_i^R$ across each data line can be attributed to higher fluid density and increased mass transfer resistance. %Conversely, the rise in $\Upsilon$ correlations may be explained by enhanced solubility. The Hildebrand solubility factor and the Reynolds number are proportional to the fluid density; hence, $\Upsilon$ can be correlated with Re.

	A more general relationship can be obtained by applying multiple linear regression instead of linear regression. The clusters in Figure \ref{fig: Correlations_Di_Re}  and \ref{fig: Correlations_Gamma_Re} are close to parallel, suggesting that a plane would combine all the data points. The Reynolds number and flow rate act as independent variables for $D_i^R$ and $\Upsilon$ as presented in Figures \ref{fig: Correlations_Di_Re_F} and \ref{fig: Correlations_Gamma_Re_F}. The presented correlations are valid in the whole range of investigated operating conditions.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.66\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4_correlation.png}
			\caption{Simulation results obtained at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
			\label{fig: Fit_1_4_Di_Gamma_correlation}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.66\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8_correlation.png}
			\caption{Simulation results obtained at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
			\label{fig: Fit_5_8_Di_Gamma_correlation}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.66\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12_correlation.png}
			\caption{Simulation results obtained at $3.33\times 10^{-5}$ [kg/s]}
			\label{fig: Fit_9_12_Di_Gamma_correlation}
		\end{subfigure}
		\caption{Simulation results from the modified model and correlations}
		\label{fig: Fit_Di_Gamma_correlation}
	\end{figure}

	The correlations are later used against the original dataset to show that the correlations can reproduce the results with satisfactory accuracy. Figure \ref{fig: Fit_Di_Gamma_correlation} shows the results of the simulations with incorporated correlations. A good agreement between simulation results and the dataset can be observed. If Figures \ref{fig: Fit_Di_Gamma} and \ref{fig: Fit_Di_Gamma_correlation} are compared, a decrease in the accuracy of simulations can be observed. Such a behaviour is expected due the bias–variance trade-off, which describes the relationship between a model's complexity and the accuracy of its predictions.

	%The parameter estimation results are compared to the work of \citet{Povh2001}, who fitted the Sovova model to the same dataset. It should be noted that the \citet{Povh2001} use as the initial solute mass ratio a value of 10\% above the total amount of extract for every experimental, while in this work, the initial conditions are the same for all the experiments as explained above. Contrary to this work, \citet{Povh2001} has not used any numerical solver in his work but rather a combination of analytical methods and a trial and error procedure. \citet{Povh2001} stated that 'the direct fitting of experimental data to the Sovova's model produced parameters that could not be accepted after a careful physical interpretation of the system'. The parameters found in this work seem to have a physical interpretation, and their values are in the excerpted range.

	%\citet{Rahimi2011} fitted the same dataset to a model with desorption–dissolution–diffusion mechanism. To decrease the number of parameters to be found, \citet{Rahimi2011} applied a set of correlations. The remaining parameters were found using a genetic algorithm to solve the parameter estimation problem for each experiment separately. The results obtained by \citet{Rahimi2011} show that the desorption–dissolution–diffusion model cannot reproduce the yield data. The desorption–dissolution–diffusion model and the model used in this work are structurally similar, with the main difference of $\gamma$ function. The $\gamma$ function increases the model's flexibility and allows it to obtain a better fit.

	%For every single experiment, \citet{Povh2001} and \citet{Rahimi2011} delivered a set of independent parameters. This work combines the parameters obtained from each experiment to get a single correlation valid for the whole range of investigated operating conditions.

	The parameter estimation results are compared against those presented by \citet{Povh2001}, who applied the Sovova model to the same dataset. It is important to note that \citet{Povh2001} use as the initial solute mass ratio a value of 10\% above the total amount of extract for every experimental, while in this work, the initial conditions are the same for all the experiments. In contrast to this work, \citet{Povh2001} did not utilize numerical solvers but used a mix of analytical methodologies and trial-and-error procedures. \citet{Povh2001} remarked that 'the direct fitting of experimental data to the Sovova's model produced parameters that could not be accepted after a careful physical interpretation of the system'. The parameters identified in this study seem to have a physical interpretation and are within the expected range.

	\citet{Rahimi2011} analysed the same dataset using the desorption–dissolution–diffusion model. To decrease the number of unknown parameters, \citet{Rahimi2011} applied a set of empirical correlations. The remaining parameters were determined through the use of a genetic algorithm to solve the parameter estimation problem for each experiment individually. Results obtained by \citet{Rahimi2011} shows that the desorption–dissolution–diffusion model fails to reproduce the yield data. The main difference between the model employed by \citet{Rahimi2011} and the one in this study is the $\gamma$-function. The $\gamma$-function increases the model's flexibility by adjusting $D_i$ and allows it to obtain a better fit.

	\citet{Povh2001} and \citet{Rahimi2011} delivered a set of independent parameters for every single experiment. This work combines the parameters obtained from each experiment to get a single correlation valid for the whole range of investigated operating conditions.

>>>>

	To solve the parameter estimation problem, the single shooting method was used to transform the boundary-value problem into the initial value problem and to formulate the non-linear programming problem. This non-linear optimisation task was tackled using the CasADi framework (\citet{Andersson2018}). Each time series was fitted separately to the model with the linear extraction kinetics (Equation \ref{Model_kinetic_no_sat}). The parameter estimation problem was solved multiple times with varying parameter initial values to identify the global minimum. In the case of linear, two parameters remain to be determined: the partition coefficient $k_m$ and the internal diffusion coefficient $D_i$. \citet{Rahimi2011} analysed the same dataset and reported Peclet numbers between 290 and 400. Large Peclet number suggest that the advection term dominates the mass transfer, and the axial diffusion is negligible, which is one of the modelling assumptions.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.85\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_Space_Linear_Dataset_1.png}
			\caption{The linear kinetic model \\ ~}
			\label{fig: Fit_1_linear}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.85\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
			\caption{The modified model}
			\label{fig: Fit_1_Di_Gamma}
		\end{subfigure}
		\caption{Parameter space for experiment 1}
		%\label{fig: Fit_Di_Gamma}
	\end{figure}

	Figure \ref{fig: Fit_1_linear} shows the parameter space and corresponding values of the cost function for experiment 1 ($40^\circ C$, 100 bar and 6.67$\times 10^{-5}$ kg/s). As the cost function is to be minimized, the lowest value of $-\ln(L)$ indicate the best fit. A black vertical stripe at $D_i \approx 0.2$ can be observed. That stripe indicates the existence of the optimal value of the $D_i$. In the direction of $k_m$, the cost function is almost flat, which suggests that any value of $k_m$ above 0.1 fits the data equally well. If $k_m$ can be an arbitrary point, then it can grow to infinity, which suggests that the solvent is far from the saturation, and the model can be simplified. The model reduction can be introduced by considering the limit of $k_m$:

@@

	In the scenario previously discussed, the fitting outcomes were not deemed satisfactory. Building upon the concepts underlying the Broken-and-Intact and Shrinking Core models (detailed in Chapter \ref{CH: Gamma_Function}), the $\gamma$-function is introduced to capture the decreasing extraction kinetics. The correction factor is combined with the simplified linear model, resulting in a two-parameter model ($D_i^R$ and $\Upsilon$) as given by Equation \ref{Model_kinetic}. Figure \ref{fig: Fit_1_Di_Gamma} shows the parameter space and the corresponding cost function values.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.85\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4.png}
			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
			\label{fig: Fit_1_4_Di_Gamma}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.85\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8.png}
			\caption{Parameter estimation results at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
			\label{fig: Fit_5_8_Di_Gamma}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.85\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12.png}
			\caption{Results of parameter estimation for experiments at $3.33\times 10^{-5}$ [kg/s]}
			\label{fig: Fit_9_12_Di_Gamma}
		\end{subfigure}
		\caption{Parameter estimation results obtained from the modified model}
		\label{fig: Fit_Di_Gamma}
	\end{figure}

@@

@@

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.85\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Di_Re.png}
			\caption{Linear regression $D_i^R = f(Re)$}
			\label{fig: Correlations_Di_Re}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.85\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Gamma_Re.png}
			\caption{Linear regression $\Upsilon = f(Re)$}
			\label{fig: Correlations_Gamma_Re}
		\end{subfigure}
		\caption{Linear correlations between parameters}
		%\label{fig: Correlations_surface}
	\end{figure}

	In Figures \ref{fig: Correlations_Di_Re} and \ref{fig: Correlations_Gamma_Re}, two distinct data clusters emerge, each corresponding to a different mass flow rate. Despite the linear trends observed in both sets of correlations, the correlations for $D_i^R$ exhibit a decline with increasing $Re$, whereas those for $\Upsilon$ show an upward trend with $Re$. The decrease in $D_i^R$ across each data line can be attributed to higher fluid density and increased mass transfer resistance.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.85\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Di_Re_F.png}
			\caption{Multiple linear regression $D_i^R = f(Re, F)$}
			\label{fig: Correlations_Di_Re_F}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.85\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Gamma_Re_F.png}
			\caption{Multiple linear regression $\Upsilon = f(Re, F)$}
			\label{fig: Correlations_Gamma_Re_F}
		\end{subfigure}
		\caption{Empirical correlations between parameters}
		%\label{fig: Correlations_surface}
	\end{figure}

	A more general relationship can be obtained by applying multiple linear regression instead of linear regression. The data clusters in Figure \ref{fig: Correlations_Di_Re} and \ref{fig: Correlations_Gamma_Re} are close to parallel, suggesting that a plane would combine all the data points. The Reynolds number and mass flow rate act as independent variables for $D_i^R$ and $\Upsilon$ as presented in Figures \ref{fig: Correlations_Di_Re_F} and \ref{fig: Correlations_Gamma_Re_F}. The presented correlations are valid in the whole range of investigated operating conditions. The correlations are later tested against the original dataset to show that the correlations can reproduce the results with satisfactory accuracy. Figure \ref{fig: Fit_Di_Gamma_correlation} shows the results of the simulations with incorporated correlations. A good agreement between simulation results and the dataset can be observed. If Figures \ref{fig: Fit_Di_Gamma} and \ref{fig: Fit_Di_Gamma_correlation} are compared, a decrease in the accuracy of simulations can be observed. Such a behaviour is expected due to the bias-variance trade-off, which describes the relationship between a model's complexity and the accuracy of its predictions.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.85\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4_correlation.png}
			\caption{Simulation results obtained at $6.67\times 10^{-5}$ [kg/s] and temperature of 40 $[^\circ C]$}
			\label{fig: Fit_1_4_Di_Gamma_correlation}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.85\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8_correlation.png}
			\caption{Simulation results obtained at $6.67\times 10^{-5}$ [kg/s] and temperature of 30 $[^\circ C]$}
			\label{fig: Fit_5_8_Di_Gamma_correlation}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.85\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12_correlation.png}
			\caption{Simulation results obtained at $3.33\times 10^{-5}$ [kg/s]}
			\label{fig: Fit_9_12_Di_Gamma_correlation}
		\end{subfigure}
		\caption{Simulation results from the modified model and correlations}
		\label{fig: Fit_Di_Gamma_correlation}
	\end{figure}

	The parameter estimation results are compared against those presented by \citet{Povh2001}, who applied the Sovova model to the same dataset. It is important to note that \citet{Povh2001} use as the initial solute mass ratio a value of 10\% above the total amount of extract for every experiment, while in this work, the initial conditions are the same for all the experiments. In contrast to this work, \citet{Povh2001} did not utilise numerical solvers but used a mix of analytical methodologies and trial-and-error procedures. \citet{Povh2001} remarked that 'the direct fitting of experimental data to Sovova's model produced parameters that could not be accepted after a careful physical interpretation of the system'. The parameters identified in this study seem to have a physical interpretation and are within the expected range.

	\citet{Rahimi2011} analysed the same dataset using the desorption–dissolution–diffusion model. To decrease the number of unknown parameters, \citet{Rahimi2011} applied a set of empirical correlations. The remaining parameters were determined using a genetic algorithm to solve the parameter estimation problem for each experiment individually. Results obtained by \citet{Rahimi2011} show that the desorption–dissolution–diffusion model fails to reproduce the yield data. The main difference between the model employed by \citet{Rahimi2011} and the one in this study is the $\gamma$-function. The $\gamma$-function increases the model's flexibility by adjusting $D_i$ and allows it to obtain a better fit.

	\citet{Povh2001} and \citet{Rahimi2011} delivered a set of independent parameters for every experiment. This work combines the parameters obtained from each experiment to get a single correlation valid for the whole range of investigated operating conditions.
